Cost- and Deadline-constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-01-10 paper/paper.tex
Paper: Update SPSS algorithm

\begin{algorithm}
\caption{Plan Ensemble}
\label{alg:admit}
\begin{algorithmic}[1]
\Procedure{PlanEnsemble}{$W,b,d$}
    \State $P\gets empty\ plan$
    \State $A\gets \emptyset$ \Comment{Set of admitted DAGs}
    \For{$w\ in\ W$}
        \State $P^\prime \gets$\ \Call{PlanDAG}{$w,P,d$}
        \If{$P^\prime\ is\ a\ valid\ plan$}
            \If{$Cost(P^\prime) \le b$}
                \State $P\gets\ P^\prime$ \Comment{Accept new plan}
                \State $A \gets A\ +\ w$ \Comment{Admit w}
            \EndIf
        \EndIf
    \EndFor
    \State \textbf{return} $P,A$
\EndProcedure
\end{algorithmic} 
\end{algorithm}

\begin{algorithm}
\caption{PlanDAG}
\label{alg:plandag}
\begin{algorithmic}[1]
\Procedure{PlanDAG}{$w,P,d$}
    \State $P^\prime\gets \emptyset$
    \State assign each task in w to its cheapest resource type
    \State $cp \gets\ CriticalPath(w)$
    \While{$cp > d$}
        \State upgrade resource type of task with greatest improvement in runtime for least cost
        \State $cp \gets\ CriticalPath(w)$
    \EndWhile
    \State \Call{DeadlineDistribution}{w,d}
    \For{$t\ in\ w\ sorted\ by\ Deadline(t)$}
        \State choose resource r in $P^\prime$ that minimizes Cost(t)
        \If{$AFT(t,r) < Deadline(t)$}
            \State Schedule(t,r)
        \Else
            \State provision a new resource r
            \State Schedule(t,r)
        \EndIf
    \EndFor
    \State \textbf{return} $P^\prime$
\EndProcedure
\end{algorithmic} 
\end{algorithm}

\begin{algorithm}
\caption{Deadline Distribution}
\label{alg:deadlinedistribution}
\begin{algorithmic}[1]
\Procedure{DeadlineDistribution}{$w,d$}
    \State assign $Level(t)$ to each task t in w
    \For{$level\ l\ in\ w$}
        \State $Tasks(l) \gets$ number of tasks in l
        \State $Runtime(l) \gets$ runtime of tasks in l
    \EndFor
    \State $T \gets$ total number of tasks in w
    \State $R \gets$ total runtime of tasks in w
    \State $CP \gets$ critical path of w
    \For{$level\ l\ in\ w$}
        \State $r \gets \alpha * (Runtime(l)/R)$
        \State $t \gets (1-\alpha) * (Tasks(l)/T)$
        \State $FT(l) \gets (r + t) * (d - CP)$
    \EndFor
    \For{$task\ t\ in\ w$}
        \State $est \gets 0$
        \For{p in Pred(t)}
            \State $est \gets Deadline(p)$
        \EndFor
        \State $Deadline(t) \gets est + RT(t) + FT(Level(t))$
    \EndFor
\EndProcedure
\end{algorithmic} 
\end{algorithm}

>>>>

\begin{algorithm}
\caption{Ensemble planning algorithm}
\label{alg:admit}
\begin{algorithmic}[1]
\Require W: workflow ensemble, b: budget, d: deadline
\Ensure Schedule as much of W as possible given b and d
\Procedure{PlanEnsemble}{$W,b,d$}
    \State $P\gets empty\ plan$
    \State $A\gets \emptyset$ \Comment{Set of admitted DAGs}
    \For{$w\ in\ W$}
        \State $P^\prime \gets$\ \Call{PlanDAG}{$w,P,d$}
        \If{$P^\prime\ is\ a\ valid\ plan$}
            \If{$Cost(P^\prime) \le b$}
                \State $P\gets\ P^\prime$ \Comment{Accept new plan}
                \State $A \gets A\ +\ w$ \Comment{Admit w}
            \EndIf
        \EndIf
    \EndFor
    \State \textbf{return} $P,A$
\EndProcedure
\end{algorithmic} 
\end{algorithm}

\begin{algorithm}
\caption{DAG planning algorithm}
\label{alg:plandag}
\begin{algorithmic}[1]
\Require $w$: DAG, $P$: current plan, $d$: deadline
\Ensure Create plan for $w$ that minimizes cost and meets deadline $d$
\Procedure{PlanDAG}{$w,P,d$}
    \State $P^\prime\gets$ copy of $P$
    \State \Call{DeadlineDistribution}{w,d}
    \For{$t\ in\ w\ sorted\ by\ Deadline(t)$}
        \State Choose resource r in $P^\prime$ that minimizes Cost(t)
        \If{$AFT(t,r) < Deadline(t)$}
            \State Schedule(t,r)
        \Else
            \State Provision a new resource r
            \State Schedule(t,r)
        \EndIf
    \EndFor
    \State \textbf{return} $P^\prime$
\EndProcedure
\end{algorithmic} 
\end{algorithm}

\begin{algorithm}
\caption{Deadline distribution algorithm}
\label{alg:deadlinedistribution}
\begin{algorithmic}[1]
\Require w: DAG, d: global deadline
\Ensure Assign sub-deadlines to each task in w
\Procedure{DeadlineDistribution}{$w,d$}
    \State assign $Level(t)$ to each task t in w
    \For{$level\ l\ in\ w$}
        \State $Tasks(l) \gets$ number of tasks in l
        \State $Runtime(l) \gets$ runtime of tasks in l
    \EndFor
    \State $T \gets$ total number of tasks in w
    \State $R \gets$ total runtime of tasks in w
    \State $CP \gets$ critical path of w
    \For{$level\ l\ in\ w$}
        \State $r \gets \alpha * (Runtime(l)/R)$
        \State $t \gets (1-\alpha) * (Tasks(l)/T)$
        \State $FT(l) \gets (r + t) * (d - CP)$
    \EndFor
    \For{$task\ t\ in\ w$}
        \State $est \gets 0$
        \For{p in Pred(t)}
            \State $est \gets Deadline(p)$
        \EndFor
        \State $Deadline(t) \gets est + RT(t) + FT(Level(t))$
    \EndFor
\EndProcedure
\end{algorithmic} 
\end{algorithm}
